\newpage
\chapter{Introduction}

\section{Introduction}
In the modern era users demand personalized experiences. They required information that is relevant, individualized and provide them with an accurate recommendation for the new content and new products based on their previous activities. People usually spent hours for searching relevant product over the internet. Any application or website that would fail to deliver on these demands will quickly see its users collecting at the digital door.\\
The purpose of this project is to provide personalized experience to the user while searching data. Users, when searched data will inform about its relevance as a feedback and according a customized search, will be provided to the users. In our project we are going to implement a personalization system in which user will browse the content according to their requirement then from the searched information they will provide feedback for the relevance of that where the data will be processed through various stages as editorial planning, content reusing, navigation and content hierarchy.

\section{Purpose}
The purpose of this project is to provide personalized experience to the user while searching data. Users when searched data will inform about its relevance as a feedback and according a customized search will be provided to the users.


\section{Problem-Statement}
To find useful and relevant information based on the keyword typed and the user’s interest which is found out using different methods of personalization of information and algorithms.
\section{Scope}
In our project we are going to implement a personalization system in which user will browse the content according to their requirement then from the searched information they will provide feedback for the relevance of that where the data will be processed through various stages as editorial planning, content reusing ,navigation and content hierarchy, Users flow and calls to action, content structure Taxonomy and Metadata ,Content development and production .This will result in the customized data to the user.
\section{Objectives}
The main objective of this project is to provide personalized
experience to the user while searching data. Users when
searched data will inform about its relevance as a feedback
and according a customized search will be provided to the
users.Also we will try to find useful and relevant information
based on the keyword typed and the user’s interest which is
found out using different methods of personalization of
information and algorithms. We’ll try to save a whole bunch
of time working over the internet and provide more Relevant
data Recommendations.It focuses on consistency among the website users and every user gets a
personalized experience of the website but at the same time
we cannot get it right every time that's what's going on in the
mind of the user.It comes with great
customer service and satisfaction although it comes at its own
cost for the users.
\vspace{10mm}
\hrule