\newpage
\chapter{Theory And Relevance}

\section{Web Scraping:}
Web scraping is the process of collection of structured web data in an structured fashion. It's also called web data extraction. There are many use cases of web scraping which include  price intelligence, monitoring new, price monitoring, generation of lead and market research among many others.
	Web scraping a web page involves extracting data and results from it that are relevant. Therefore, web crawling is one of the main component of web scraping, so as to extract pages for later processing. Once fetched, then extraction can take place. These contents of pages may be searched, parsed, reformatted, its data copied into a spreadsheet etc. Web scrapers typically extracts relevant data out of a page, to make use of it for another purpose by studying data. 
This is an automatic version of gathering well-structured data
from web pages.In other terms it is said to be web-data extraction. Web
scraping a web page implies fetching it, and extracting data
from it. Fetching is actually the downloading of a page.
Hence, web crawling is a major component of web scraping,
to fetch pages for further processing. Once after fetching the data, then
data extraction can take place . Web Crawling actually consists
of a crawler that automatically searches and explores content
on the web. Crawlers are fundamentally programmed for
repetitive steps and actions such that web browsing and
searching gets automated. Some websites contain a massive
amount of invaluable data. It’s a very tedious job to manually
extract this huge amount of data. Web Scraping extracts this
huge amount of data and then exports it to a format that is
more convenient for the user ( For Eg. Excel, pdf etc).
\section{Web Usage mining :}
Web usage mining is the application of data mining techniques to discover interesting usage pattern from the Web data in order to study and better satisfy the needs of Web-based applications. Usage data captures the identity or origin of Web users along with their browsing behavior at a Web site.Web usage mining is a subcategory of data mining which is
used for recognizing usage patterns and trends from web data.
This is a combination of different applied techniques, to
unravel informative usage trends from data taken over the
internet. Web usage mining understands the requirements and
needs of web based applications and It is then analyzed,
understood and is then fed to web based applications. This
type of data captures the identity or emergence of Web users
along with their behavior of how they browse and browsing
history, at browser level as well as website level\\
Web usage mining can be classified depending on the kind of data-usage considered:\\

a. Web server data: The user information are collected by the Web server.The typical user data includes IP address of site, page data etc.\\
b. Application server data: Many Commercial application servers have significant functionality so as to enable applications to be built on top of them with minimal effort. A key feature of this is the ability to understand various kinds of business events and thus log them in application server data.\\
c. Application level data: Many new kinds of events and actions can be defined in an application, and thus logging can be turned manually on  for them thus generating past searches of these specially defined actions. Many back-end application requires a combo of one or more of these techniques applied.\\
\section{Web personalization :}
Web Personalisation or Personalisation of information is a
web mining technique which helps the customers to find
relevant information to the searches they make on the internet.
The main focus of this project is on providing the users the
provision of bettering their web searches and personalizing
according to their experience and also help them in
personalizing the information with some external help such as
recommendation system, search feedback, pages indexing etc.\\
After studying and analyzing many paper and articles on web,
we found that the main problem in the system is :\\
a. Optimized Landing Pages\\
b. More Relevant Content Recommendations\\
c. Increase in User Engagement on the Website.\\
d. Unsatisfactory Search Results\\
e. Inefficient methods of getting useful information\\
f. Reduce the time required for finding useful results\\
\vspace{10mm}
\hrule